---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Estimating contact-adjusted immunity levels against measles in South Korea and prospects for maintaining elimination status"
```

# Estimating contact-adjusted immunity levels against measles in South Korea and prospects for maintaining elimination status

This repository contains the data and code for our paper:

> June Young Chun, Wan Beom Park, Nam Joong Kim, Eun Hwa Choi, Sebastian Funk, Myoung-don Oh (2019). _`r Title`_.

### How to download or install

You can download the compendium as a zip from from this URL: <https://github.com/sbfnk/sk.measles/archive/master.zip>

Or you can install this compendium as an R package, `sk.measles`, from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("sbfnk/sk.measles")
```

### Included data sets

The package includes all the data sets required in order to reproduce the results: Measles seroprevalence in South Korea as measured in 2014 (`sk_seroprevalence`), vaccinaton coverage (`sk_mcv_coverage`), demographics (`sk_population`) and a contact matrix derived from a study in Japan (`japan_contacts`).

### Table and figures

To generate Table 1 from the paper, run

```{r eval=FALSE}
table1(japan_contacts)
```

To generate the scenarios of increasing vaccination in different age groups used for Figure 2, use

```{r eval=FALSE}
scenarios(japan_contacts)
```

### Sensitivity analysis

To conduct sensitivity analysis where the 20-29 age group is split into two equally sized age groups, use the `split_20_29` function:

```{r eval=FALSE}
split_contacts <- split_20_29(japan_contacts)
```

Replacing `japan_contacts` with `split_contacts` in the commands above runs the same analyses, but with the contact matrix with split age groups.

To conduct sensitivity analysis where equivocal samples are interpreted as negative, use `equivocal="negative"` with any of the commands above.
